---
title       : Reproducible Pitch Presentation
subtitle    : Course "Developing Data Products" at Coursera
author      : Milen Angelov
job         : COO at a waterfall
logo        : logo.jpg
framework   : io2012
widgets     : []
github:
  user: pimpf
  repo: Developing_Data_Products

--- bg:#EEE
## About the application
<p style="font-size:20px"><i>This application tends to do a very basic demonstration of the caret package which is a set of functions that attempt to streamline the process for creating predictive models.</i>
More information about cared package could be found <a href="http://topepo.github.io/caret/index.html">here</a>
</p>
## About caret package
<p style="font-size:20px"><b>caret</b> has several functions that attempt to streamline the model building and evaluation process, as well as feature selection and other techniques.
One of the primary tools in the package is the train function which can be used to:
<ul>
<li> Evaluate, using resampling, the effect of model tuning parameters on performance</li>
<li> Choose the "optimal" model across these parameters</li>
<li> Estimate model performance from a training set</li>
</ul>
There are options for customizing almost every step of this process.
</p>

--- 

## What the application does
<p style="font-size:20px">
This small application uses <b>iris</b> dataset and implements the following functionality of caret package:<br/>
- Split the data into two groups: a training set and a test set<br/>
- Use trainControl to modify resampling method<br/>
- Tune a model using selected algorithm<br/>
- Predict new samples using testing set<br/>
- Compute the confusion matrix and associated statistics for the model fit
</p>
## How to use it
<p style="font-size:20px">
1. Select ratio of spliting data using slider<br/>
2. Choose train control method from the drop-down menu<br/>
3. Select tune model algorithm from the radio button group</br>
4. Hit "Do prediction button". It may take few seconds before Confusion Matrix apppear on the right side.</p>

---
## ui.R
<p style="font-size:16px">
In this script the layout is defined. Page is created with fluid layout fluidPage. Title Panel is at the top. sidebarLayout is used to separate the page into two panels.
The following widgets are positioned on the right: <b>sliderInput</b> is used to define ratio of spliting dataset, <b>selectInput</b> to choose train control, <b>radioButtons</b> to select a train method and <b>actionButton</b> to trigger calculations.<br/>
On the left are printed results of the calculation with <b>verbatimTextOutput</b>
</p>
## server.R
<p style="font-size:16px">
For computation the application needs all parameters to be set. In order not to compute on each iteraction reactive expressions are used and within <b>renderPrint</b> calculation is executed in "isolation". Also some methods take longer, for that reason and for better visual present progress bar is included with <b>withProgress</b> function.</p>
```{r class="fragment", echo=TRUE, error=FALSE, message=FALSE, eval=FALSE, results='hide'}
 output$predictions <- renderPrint({
        isolate({
            withProgress(message = 'Progress...', value = 0, {
                ......
```


---
## How results are calculated
<p style="color:red;font-size:16px"><i>Result of the computation below is not included as it takes a lot of space</i></p>
```{r class="fragment", echo=TRUE, error=FALSE, message=FALSE, eval=TRUE, results='hide'}
library(caret);
library(rpart);
data(iris);
# Do train/test split of the dataset
trainIndex <- createDataPartition(iris$Species, p = .75, list = FALSE);
data_train <- iris[ trainIndex,];
data_test <- iris[-trainIndex,];
# Define train control
tc <- trainControl(method="boot", number=100);
# Train model
model <- train(Species~., data=data_train, trControl=tc, method="rpart");
# Make predictions
predictions <- predict(model, newdata = data_test);
# Summarize results and show it on the right
confusionMatrix(predictions, data_test$Species);
```



